Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-20 article/article.tex
(+) objective function and cost function
+ smaller subsubsection and not bold

% Allows customization of titles
\usepackage{titlesec}
% Roman numerals for the sections
\renewcommand\thesection{\Roman{section}}
% roman numerals for subsections
\renewcommand\thesubsection{\roman{subsection}}
% Change the look of the section titles
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{}
% Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{}

@@

It is now possible to assign a cost to each partition. This cost is linear
regarding $c_+$, $c_=$, $c_-$ and $n$ (cardinal of the partition $P$). The
partition cost is defined as follow:
$$
C(P, t) = \alpha c_+ + \beta c_= + \gamma c_- +\lambda n
$$

The parameters $\alpha$, $\beta$, $\gamma$ and $\lambda$ (all positive)
determine a priority on which parameter to optimize. For instance, a high
value $\alpha$ help to
minimize $c_+$, hence the overall number of sectors with too much tafic.
In a real application, it maybe interesting to order those parmaeters as
follow : $\alpha > \lambda > \beta > \gamma$.

@@

In an operational context, each reconfiguration raise the workload for
controllers. This trend needs to be considered and a transition cost needs to
be defined for this matter. A transition is (TODO), and the transition cost is
then:
$$
C_{tr}(P_1, P_2) =
\left\{
\begin{array}{l}
    0 \qquad if \qquad P_1 = P_2 \\
    1 \qquad otherwise
\end{array}
\right.
$$

>>>>

% Allows customization of titles
\usepackage{titlesec}
% Roman numerals for the sections
\renewcommand\thesection{\Roman{section}}
% roman numerals for subsections
\renewcommand\thesubsection{\roman{subsection}}
% Change the look of the section titles
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{}
% Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{}
\titleformat{\subsubsection}[block]{\normal}{\thesubsection.}{1em}{}

@@

It is now possible to assign a cost to each partition. This cost is linear
regarding $c_+$, $c_=$, $c_-$ and $n$ (cardinal of the partition $P$). The
partition cost is defined as follow:
\begin{equation}
C(P, t) = \alpha c_+ + \beta c_= + \gamma c_- +\lambda n  
\end{equation}

The parameters $\alpha$, $\beta$, $\gamma$ and $\lambda$ (all positive)
determine a priority on which parameter to optimize. For instance, a high
value $\alpha$ help to
minimize $c_+$, hence the overall number of sectors with too much tafic.
In a real application, it maybe interesting to order those parmaeters as
follow : $\alpha > \gamma > \beta > \lambda$.

@@

In an operational context, each reconfiguration raise the workload for
controllers. This trend needs to be considered and a transition cost needs to
be defined for this matter. A transition is (TODO), and the transition cost is
then:
\begin{equation}
  C_{tr}(P_1, P_2) =
\left\{
\begin{array}{l}
    0 \qquad if \qquad P_1 = P_2 \\
    1 \qquad otherwise
\end{array}
\right.
\end{equation}

\subsection{Objective function}

With a cost defined for partition and transition, it is now possible to
aggregate everything in order to build a cost function over an entire
path. For a path ($path = [P_0, ..., P_n]$) with a time from $t_0$ to $t_n$,
the cost function is given by:
\begin{equation}
  \begin{split}
  f(path) = C(P_0, t_0) + \sum_{i = 1}^{n} [C(P_i, t_i) +\\ \theta \times C_{tr}(P_{i-1}, P_i)]   
  \end{split}
\end{equation}

with $\theta > 0$ a parameter to determine.
This is the imediate function to minimize in the A$^*$ algorithm.

The Monte Carlo Tree search algorithm maximize a objective function. This function
represent a potential reward over a path, i.e. a list of partitions over time.
Given the loss function defined previously, the target function can be
construct as:
\begin{equation}
  \psi(path) = \frac{1}{f(path)}
\end{equation}
